A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-06-24 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}
    \centering
		\subfloat[\centering Circles pattern image, in image plane of projector (detected 2D circles pattern center points overlain).]{{\includegraphics[height=3.25cm]{images/circles.png} }}
    \qquad
    \subfloat[\centering Projector calibration image (one for each target location), in image plane of camera (detected 2D projected circles pattern center points and chessboard corners overlain).]{{\includegraphics[height=3.25cm]{images/detections.png}}}
		\caption{Recovering 2D positions in support of projector calibration. (a) 2D positions of the 2D-3D correspondences to be used for calibrating the projector are obtained by detecting---in the image plane of the projector---the circle centers in the circles pattern image projected by the projector to each of the target locations in the scene plane. (b) For each such target location, an image is acquired from the viewpoint of the camera and the circle centers of the projected circles pattern are detected. A chessboard pattern to be used for recovering the local scene plane is placed near the projected pattern, whose corners are likewise detected.} %At this stage, the chessboard is used to recover the local scene plane for each target location. Since the projected circles pattern lies in this plane, we are in a subsequent step able to rely on that plane to derive the 3D positions corresponding to the 2D projected circles pattern center points detected in the image.
    \label{fig:2d}
\end{figure}

@@

\paragraph{Projector calibration} As in the case of camera calibration, projector calibration relies on 2D-3D correspondences, yet we obtain them in this case by projecting a pattern of circles. We rely on an algorithm to detect the circle pattern center points in the circles pattern image in the image plane of the projector, giving the 2D positions of our 2D-3D correspondences (cf.\ Figure~\ref{fig:2d}(a)). We project the circles pattern image to each of the target locations, and use the camera to acquire a projector calibration image for each. Given a projector calibration image, we again detect the centers of the \textit{projected} circles pattern (cf.\ Figure~\ref{fig:2d}(b)); given the scene plane (the recovery of which we shall turn to in the paragraph that follows) and such a 2D circle center $\mathbf{x}$, its 3D correspondence is obtained by intersecting the back-projection of $\mathbf{x}$ with the scene plane (cf.\ Figure~\ref{fig:3d}). Since the algorithm that yields 2D circle centers does so in a consistent ordering, we thus obtain the 2D-3D correspondences between the projector's image plane and the scene required for projector calibration, yielding the projector calibration matrix~$\mathtt{K}_\text{proj}$.

@@

If the projector is calibrated and its pose relative to the scene plane is known, a `virtual' projector (with the same calibration $\mathtt{K}$ and lens distortion coefficients) can be placed elsewhere relative to the scene plane. If we for a moment imagine that the projector---at its recovered `original' pose---functions as a camera,\footnote{Recall that the calibration matrix~$\mathtt{K}$ enables computing the projection of a scene point to the image plane (the function of a camera), or computing the back-projection of a pixel in the image plane, giving a ray into the scene (along which a projector illuminates the scene with the given pixel).} then (i) projecting an image to the scene plane \textit{from the viewpoint of the virtual projector} and (ii) acquiring the resulting projected image from the viewpoint of the recovered {original projector} gives the desired distortion that is to be applied, if the image is to be projected from the viewpoint of the original projector. Projecting an image distorted in this manner to the scene plane \textit{from the viewpoint of the original projector} then has the same effect as projecting the undistorted image to the scene plane from the viewpoint of the virtual projector. Given the scene plane, the projector, and the virtual projector, this distortion can computed using a plane-induced homography.

>>>>

\begin{figure}
    \centering
		\subfloat[\centering Circles pattern image, in image plane of projector.]{{\includegraphics[height=3.25cm]{images/circles.png} }}
    \qquad
    \subfloat[\centering Projector calibration image (one for each target location), in image plane of camera.]{{\includegraphics[height=3.25cm]{images/detections.png}}}
		\caption{Recovering 2D positions in support of projector calibration. (a) 2D positions of the 2D-3D correspondences to be used for calibrating the projector are obtained by detecting---in the image plane of the projector---the circle centers in the circles pattern image projected by the projector to each of the target locations in the scene plane. (b) For each such target location, an image is acquired from the viewpoint of the camera and the circle centers of the projected circles pattern are detected, in the image plane of the camera. A chessboard pattern to be used for recovering the local scene plane is placed near the projected pattern, whose corners are likewise detected. Detected 2D projected circles pattern center points and chessboard corners overlain for illustration.} %At this stage, the chessboard is used to recover the local scene plane for each target location. Since the projected circles pattern lies in this plane, we are in a subsequent step able to rely on that plane to derive the 3D positions corresponding to the 2D projected circles pattern center points detected in the image.
    \label{fig:2d}
\end{figure}

@@

\paragraph{Projector calibration} As with camera calibration, projector calibration relies on 2D-3D correspondences, yet we obtain them in this case by projecting a pattern of circles. We rely on an algorithm to detect the circle pattern center points in the circles pattern image in the image plane of the projector \cite{bradski2000opencv}, giving the 2D positions of our 2D-3D correspondences (cf.\ Figure~\ref{fig:2d}(a)). We project the circles pattern image to each of the target locations, and use the camera to acquire a projector calibration image for each. Given a projector calibration image, we again detect the circle centers of the \textit{projected} circles pattern (cf.\ Figure~\ref{fig:2d}(b)); given the scene plane (the recovery of which we shall turn to in the paragraph that follows) and such a 2D circle center $\mathbf{x}$, its 3D correspondence is obtained by intersecting the back-projection of $\mathbf{x}$ with the scene plane (cf.\ Figure~\ref{fig:3d}). Since the algorithm that yields 2D circle centers does so in a consistent ordering, we thus obtain the 2D-3D correspondences between the projector's image plane and the scene required for projector calibration, yielding the projector calibration matrix~$\mathtt{K}_\text{proj}$.

@@

If the projector is calibrated and its pose relative to the scene plane is known, a `virtual' projector (with the same calibration $\mathtt{K}$ and lens distortion coefficients) can be placed elsewhere relative to the scene plane. If we for a moment imagine that the projector---at its recovered `original' pose---functions as a camera,\footnote{Recall that the calibration matrix~$\mathtt{K}$ enables computing both (i) the projection of a scene point to the image plane (the function of a camera), or (ii) the back-projection of a pixel in the image plane, giving a ray into the scene (along which a projector illuminates the scene with the given pixel).} then (i) projecting an image to the scene plane \textit{from the viewpoint of the virtual projector} and (ii) acquiring the resulting projected image from the viewpoint of the original projector gives the desired distortion. Projecting an image distorted in this manner to the scene plane \textit{from the viewpoint of the original projector} then has the same effect as projecting the undistorted image to the scene plane from the viewpoint of the virtual projector. This distortion can computed using a plane-induced homography, computed analytically as a function of the scene plane, the projector, and the virtual projector.
